\Large \bf Security Audit of Safeplug ``Tor in a Box''

### 2014-05-28 foci/paper.tex
final submitted version of paper in foci/ folder

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{graphicx}
\usepackage{usenix,epsfig}
\usepackage{url}
\usepackage{listings}
\usepackage{subfigure}

@@

\section{Introduction}
Privacy on the Internet is becoming increasingly important as users realize how vulnerable they are to surveillance and theft of their data.  A recent Pew study listed compromised emails/accounts, harassment, and stolen Social Security Numbers, bank information, and credit card numbers as some of the results of online visibility; according to the study, 86\% of internet users have tried to become more anonymous online~\cite{pew}.  Despite this, users do not believe that they have the tools to solve this problem.

@@

\begin{itemize} \setlength{\itemsep}{.2mm}
\item The Safeplug functions as a HTTP proxy for the browser, which then uses Tor for outgoing traffic.
\item Despite the use of Privoxy as an ad-blocker, the Safeplug does nothing to prevent users' browsers from collecting both first- and third-party tracking cookies, allowing users to be de-anonymized across websites despite the presence of Tor~\cite{arvindpets}.
\item Safeplug users are vulnerable to a Cross-Site Request Forgery (CSRF) attack that allows an attacker external to their home network to modify the Safeplug settings (including silently turning off the use of Tor).
\item A malicious user within the network can modify the Safeplug settings without notifying any other devices on the network.
\item The Safeplug has a higher web request latency than that of the Tor Browser Bundle.
\item The Tor Browser Bundle provides more protection than the use of Privoxy, and therefore the use of the Safeplug.
\end{itemize}

Pogoplug made use of good security principles by using auditable open source software on their device, and has the laudable goal of making online security the standard for more users. However, there are other technologies available that aim to provide the same functionality, such as the Tor Browser Bundle; additionally, this technology is free.  In order to determine if there is a market for the Safeplug, we measure the privacy implications between the different technologies.  We show that there is little reason to use the Safeplug over the Tor Browser Bundle; in addition to the Tor network technology used in the Safeplug, the Tor Browser Bundle contains protections against tracking cookies and fingerprinting, making it an improvement over the privacy offerings of the Safeplug.

@@

\section{Background}
{\bf Safeplug.} Safeplug \cite{safeplug}, is a product that launched in December of 2013 from the cloud storage company Pogoplug, that offers any user the option of using Tor \cite{torproject} without having to know about it or how it works.  It allows users to browse the web from their own standard web browser with “complete security and anonymity” for the cheap price of \$49.  Safeplug offers Tor out of the box, with no additional software installation, by sitting between a user's router and the Internet \cite{wired}.  Pogoplug's marketing pitch centers around the protection of users' IP addresses by using Tor \cite{bittech}.

{\bf Pogoplug.} Pogoplug, a subsidary of Cloud Engines, also offers secure file server or file storage technologies for home networks, called Pogoplug.  Based on our examination of the box discussed below, we suspect that a recent version of the Pogoplug hardware was relabeled as Safeplug and simply uses different software to achieve its newly branded purpose.

\section{Design and Operation of Safeplug}

\subsection{Hardware}
Before investigating the software, we took apart one of the two Safeplug devices we purchased in order to see the physical components.  Figure~\ref{fig:top} shows the top of the board and Figure~\ref{fig:bottom} shows the bottom.  The board incorporates: (A) an SD card slot, (B) a power connector, (C) a USB slot, (D) an ethernet connector, (E) ethernet transceiver, (F) lan transformer, (G) the Marvell 88F6192 integrated controller, and (H), (I) flash memory.  The Marvell controller is from 2008 and is an ARM SoC~\cite{marvellhw}. 
%\begin{figure*}[tb]
%\centering
%\subfloat[][Top of the board inside the Safeplug device.]{
%  \includegraphics[width=.2\textwidth]{safeplug_listed_top}
%  \label{fig:top}
%}
%\qquad
%\subfloat[][Bottom of the Board inside the Safeplug device.]{
%  \includegraphics[width=.2\textwidth]{safeplug_hardware_new}
%  \label{fig:bottom}
%}
%\caption{Safeplug circuit board after the teardown.  The explanation of the components is in the text.}
%\label{fig:circuit}
%\end{figure*}

\begin{figure}[ht]
 \centering
 \subfigure[Top of board.]{
  \includegraphics[width=.2\textwidth]{safeplug_listed_top}
   \label{fig:top}
   }
 \subfigure[Bottom of board.]{
  \includegraphics[width=.2\textwidth]{safeplug_hardware_new}
   \label{fig:bottom}
   }
 \label{fig:circuit}
 \caption[Safeplug circuit board after the teardown.  The explanation of the components is in the text.]{%
  Safeplug circuit board after the teardown.  The explanation of the components is in the text.}
\end{figure}

\subsection{Software on the Safeplug}
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Software and the corresponding version numbers on the Safeplug as of May 2014.}
\label{versions}
\begin{center}
  \begin{tabular}{|l|c|c|c|}
    \hline
    Safeplug Software & Version & Date & Up To Date\\ \hline
    Linux Kernel & 2.6.31.8 & 2009 & No\\ \hline
    Lighttpd Web Server & 1.4.33 & 2013 & No\\ \hline
    Privoxy Proxy & 3.0.21 & 2013 & Yes\\ \hline
    Tor & 0.2.3.25 & 2012 & No\\ \hline
    Dropbear sshd & v0.52 & 2008 & No\\ \hline
  \end{tabular}
\end{center}
\end{table}

Table \ref{versions} shows the software used by the device, the corresponding version of the software, as well as the date of that versions release and if it is up to date.  There are many known vulnerabilities in the pieces of software that are not up to date.

@@

When a user modifies the settings page, Javascript on the settings page generates a POST request to {\tt xspctrl}, which is a script running via CGI in Lighttpd. The CGI handler copies a number of environment variables, and then forks and runs {\tt xspctrl} via {\tt execve} (in the constructed environment). {\tt xspctrl} is a shell script with a method for each settings change; these methods execute any necessary Safeplug binary files (go\_update, go\_upgrade, go\_sshd, or go\_updateexceptions) and then return a HTTP response.

@@

\subsection{Networking}
The Lighttpd, Privoxy, and Dropbear software give some indication of the networking services on the device.  We used \texttt{nmap} to scan the ports.  Before the activation of the Safeplug, only ports 80 (HTTP) and 3333 (unknown purpose) are open.  After the activation, port 22 for SSH, port 80 for settings access and port 8080 for http-proxy are open.  When Tor is turned on as a relay, port 9001 is opened as well.  This corresponds with the note on the settings page about Tor relays discussed in Section \ref{port9001} below.

\subsection{Configuration on the Safeplug}
\label{spconfig}
The Safeplug configuration files can be found in \verb!/opt/xce/etc! and include \verb!sp.conf! and \verb!sp_version! and \verb!sp_torexceptions!.  The first contains all of the configuration details: whether to use Tor, whether to block ads, and whether to act as a Tor relay or exit relay. The version file is used during the call to check for updates in the \verb!xspctrl! script, and the exceptions file is used by the Privoxy configuation to control the whitelist of sites not to connect to via Tor.  These configuration files are read by the scripts in \verb!/opt/xce/etc/init.d! which enable Lighttpd, Privoxy, and Tor.  As expected, Privoxy looks at the \verb!tor!, \verb!ad-block! and \verb!exceptions! configurations, and Tor reads the \verb!sp.conf! file to determine the correct Tor configuration file (regular, relay, or exit relay).

\section{Usability}
Several aspects of the user experience of the Safeplug also affect the security of the device.  The Safeplug advertisements highlighted the ease of use, but omit important details.

@@

The Safeplug uses several pieces of open source software.  A standard term of many open source licenses states that a company that uses the open source software must list the software used and its license, as well as the open source code of their own software that uses the license.  The TOS contains a link to a page that would supposedly comply with this requirement: \url{http://pogoplug.com/home-en-developers-open-source.html} but the link is dead; instead, the reader sees a 404 error \cite{safeplug}.  This dead link was noted by some members of the Tor-talk mailing list in November 2013 and has not been fixed as of May 2014 \cite{tormailinglist}.  Pogoplug does maintain an open source page at \url{https://pogoplug.com/opensource}, which describes several pieces of software for the Safeplug: the bootloader, Linux kernel, XCE kernel support driver, glibc, BusyBox, and a Safeplug source bundle.  However, there is no way to find this page from the Terms of Service or the Safeplug website.

\subsection{Activation and Setup}
The first step was to plug Safeplug into our router and activate our device.  We followed the simple instructions, activated our device, and then ended on the configurations page.  The configurations page shows a variety of platforms and browsers, shown in Table \ref{table_example}, and links to proxy configuration instructions for each one.  The platforms presented include many popular desktop and mobile platforms.  For every browser on every client device that the user wants to protect, they must set up the Safeplug as the browser's HTTP proxy and ensure that the proxy stays set up when the browser is updated or re-installed.

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{The platforms and browsers that the Safeplug settings page provides instructions for.}
\label{table_example}
\centering
	\begin{tabular}{|c|c|}
	\hline
		Platform & Browsers \\ \hline
		Windows	& Internet Explorer, Chrome, Firefox \\ \hline
		OSX & Safari, Chrome, Firefox \\ \hline
		iOS	& Safari \\ \hline
		Android	& Chrome \\ \hline
	\end{tabular}
\end{table}

After we finished configuring our Safeplug and browser, we were taken to the Safeplug settings page.  This page is shown in Figure~\ref{fig:settings}.  This page allows the user to set a number of options on the device, including turning Tor on/off, turning ad-blocking on/off, and turning relay node ability on/off (and if on, an additional option appeared to allow the device to be an exit relay).  Additionally, the user can specify ``white-listed'' domains that will be connected to directly even if Tor is turned on, without going through the Tor network.  The Safeplug FAQ website describes this as an option for sites like banks that prevent access from foreign IP addresses\cite{safeplug}.

\begin{figure*}
  \centering
  \includegraphics[width=.65\textwidth]{settings_with_exit}
  \caption{Safeplug settings page.  The last button ``Allow Exit'' only appears if the relay option above has been turned on.}
  \label{fig:settings}
\end{figure*}

\subsection{Explanation of Tor Configuration Options}
\label{port9001}
One of Safeplug's configurations is the use of the device as a Tor relay node in the Tor network.  When the device is initially set up, the default setting is to not use it as a relay node.

The settings page describes Tor in an extremely basic way:

\begin{quotation}
``Safeplug uses the Tor network to secure your Internet connection.  Tor works by routing your Internet through a series of random destinations, much like driving a twisty, complicated route to throw off someone who is following you, making it impossible for websites and organizations to identify the source or destination of Internet traffic.''
\end{quotation}

On the other hand, it assumes a much higher level of knowledge about networks for users trying to configure a relay:
\begin{quotation}
You must forward inbound traffic on port 9001 to [IP-of-Safeplug]. For help configuring your router, click here.''
\end{quotation}

The link provided is to an advertisement-filled and confusing website.

Using Safeplug as an exit node has possible legal repercussions.  As an exit relay, all traffic that exits the node can be traced back to the Safeplug's IP address; it is likely that some of this traffic contains illegal information or is part of illicit activities.  The Tor Project recommends not running an exit relay from a user's home: ``If law enforcement becomes interested in traffic from your exit relay, it's possible that officers will seize your computer. For that reason, it's best not to run your exit relay in your home or using your home Internet connection~\cite{law}.''  Considering that the Safeplug is intended for home use, it is a poor design choice to allow the user to use it as an exit relay without providing the user with any contextual information.

\subsection{Internet Use}
\label{inetuse}

@@

Next, we examined popular webpages, with an eye for changes in the user experience.  A user would probably decide not to use Safeplug if they could not read their web pages (due to a different language), or if they could not log into their accounts (some web sites will lock a user out if they try to log in from multiple countries in a short time period).  While browsing the Internet, we experienced some pages in German and Swedish; if a user is not familiar with Tor, they may not understand why this is happening.  We were also prompted with a request to ``Enter the name of the city where you usually sign in'' when we tried to log into our Google account, indicating that Google noticed we were trying to login from an ``unusual'' location.

\subsection{Cookies}  
While browsing the Internet in a fresh browser session, we logged into a Google Account in a tab, and then subsequently went to a website that had the Google+ widget in a different tab.  When we clicked on the Google+ widget, it knew who we were; so we can confirm that a cookie associated with the login was sent to the second Google+ page.  We experienced the same situation with Facebook and its corresponding ``like'' button.  This was confirmed by using FourthParty, a plugin developed by Jonathan Mayer to collect information about cookies and other browsing data~\cite{fourthparty}.

This is clearly not the perfect ``anonymity'' that Safeplug promised in their publicity.  Although normal use does follow this model of persisting logged in status across browser tabs and sessions, a user concerned about anonymity and seeing each session coming up differently (e.g., German then Swedish) might mistakenly believe that they do not have to log out of their social media accounts to preserve their anonymity when accessing other websites.

More interesting and damaging to the user's control over their anonymity would be third-party cookies because the user cannot remove those just by logging out.  Most browsers require a trip to the browser settings to clear cookies (or not have them set in the first place).  When collecting data on the existence of third-party cookies, we analyzed two separate browsing sessions; they were both new sessions with no cookies.  One of the sessions used the ad-block feature of the Safeplug and the other did not.  After analyzing data from Fourthparty, we found many third-party cookies in both sessions.  These included cookies from: abmr.net, bizographics.com, krxd.net, and bluekai.com among many others.  The ad-block functionality on the Safeplug reduced, but did not eliminate, these third-party cookies.

@@

\subsection{Browser Fingerprinting}
We used Panopticlick~\cite{panopticlick} to examine the fingerprint of a freshly installed Firefox browser running through the Safeplug proxy.  Panopticlick found the browser to be unique, which means that websites that did fingerprinting could very accurately track, correlate, and de-anonymize user traffic without knowing the IP address or even storing a cookie.  The presence of the Safeplug, as an HTTP proxy, should be completely undetectable by the fingerprinting service because HTTP is designed to make proxies transparent.  Unlike the Tor Browser Bundle, Safeplug users do not even have the fingerprints of other users of the service to help hide their fingerprints.  Allowing the user to use their own browsers significantly increases the amount of variation and customization between users and therefore the likelihood of having a unique fingerprint.  This danger to anonymity (unlike cookies) is not even mentioned in the Safeplug FAQ page~\cite{safeplug}.

\subsection{Latency}
If the latency of web requests using the Safeplug is noticeably longer than that of normal Internet use, users may be deterred from using the device.  Similarly, if turning Tor on, but not ad-blocking, adds a significant time delay, the user may only turn on the ad-blocking feature (without Tor).  We recorded the time for a web request on the following settings:

\begin{itemize} \setlength{\itemsep}{.2mm}
\item Plain Firefox (no use of the Safeplug device)
\item Firefox, no Tor, no ad-blocking (traffic running through the Safeplug device)
\item Firefox, Tor, no ad-blocking
\item Firefox, Tor, ad-blocking
\item Firefox, no Tor, ad-blocking
\item Tor Browser Bundle with Safeplug (all settings off)
\item Tor Browser Bundle
\end{itemize}

@@

\section{Privoxy vs. Tor Browser Bundle}
The Safeplug uses two primary technologies: Tor and Privoxy.  The Tor Project has developed the Tor Browser Bundle, which is a free custom browser that uses Tor as well as other protection mechanisms to help preserve a user's privacy.  The Tor Browser Bundle may be a better solution than the Safeplug if it has fewer privacy implications.  The differentiating factor between the Safeplug and the Tor Browser Bundle is the use of Privoxy; in order to determine the effectiveness of the Safeplug in comparison to that of the Tor Browser Bundle, we must find the value of Privoxy in terms of privacy.  We ran a measurement study of the privacy implications of the use of Firefox, Firefox with Privoxy, and the Tor Browser Bundle; our data was collected by running crawls on the Alexa Top 100 sites in each of the specified browsers~\cite{alexa}.  All browser configurations were modified with Pagestats \cite{pagestats} and Cookie Manager+ \cite{cookiemonster} to aggregate information about third party requests, javascript objects, flash objects, and third party cookies.  Table \ref{tbb} shows the average number per page of: third party domains accessed, javascript objects received from third parties, flash objects received from third parties, and cookies received from third parties.

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Privacy implications of using Firefox, Privoxy, or the Tor Browser Bundle; the numbers represent the average number per page.}
\label{tbb}
\centering
	\begin{tabular}{| p{1.85cm} | p{1.3cm} | p{1.25cm} | p{.7cm} | p{1cm} |}
	\hline
		Configuration & Third Party Domains & Javascript & Flash & Cookies \\ \hline
		Plain Firefox	& 0.64 & 0.01 & 0.01 & 0.88 \\ \hline
		Privoxy & 0.72 & 0.00 & 0.01 & 0.84 \\ \hline
		Tor Browser	& 0.58 & 0.01 & 0.00 & 0.00 \\ \hline
	\end{tabular}
\end{table}

It is clear to see that the Tor Browser Bundle had the fewest privacy implications in most categories; it's interesting to note that the Tor Browser Bundle did not receive any cookies, where as both other configurations received a significant number of them.  The one category where Privoxy performed better than the Tor Browser Bundle is in the number of javascript objects received from third parties; this can be attributed to the fact that our measurements were taken using the default settings for the Tor Browser Bundle, which allows javascript (NoScript is disabled)~\cite{torproject}.  This is explained on the Tor Project's website; they explain that disabling javascript causes some web pages to break, making the browser less user-friendly.  The user has the option to enable javascript by simply clicking a button.  Our data shows that the Tor Browser is a less expensive alternative to the Safeplug, and provides more privacy protections.

\section{Vulnerabilities}
As we discovered during our software analysis, the Safeplug has a remote procedure call (RPC) capability.  This is a script called \verb!xspctrl! found in \verb!/opt/xce/html/svc!.  Functional calls to this script include the ability to enable and disable all of the Safeplug settings, including Tor, ad block, and Tor relay.  None of them require any arguments in the POST string.

\begin{figure*}
  \centering
  \includegraphics[width=.75\textwidth]{disabletor2}
  \caption{Disabling Tor as an RPC attack.}
  \label{disable}
\end{figure*}

@@

Since the RPC version of the attack just involves basic Internet tools (the ability to send a POST request), the attacker could also be any kind of device on the local network, or the local gateway if it is compromised.

@@

\section{Related Work}
To our knowledge, there has been no other study analyzing the security of Pogoplug's Safeplug device.  However there has been much prior research on the primary technology that the device uses, Tor, as well as the vuvlnerability of fingerprinting.

>>>>

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{graphicx}
\usepackage{usenix,epsfig}
\usepackage{url}
\usepackage{listings}
\usepackage{subfigure}
\usepackage{paralist}
%\usepackage[compact]{titlesec}
%\titlespacing{\section}{0pt}{2ex}{2ex}
%\titlespacing{\subsection}{0pt}{1ex}{1ex}
%\titlespacing{\subsubsection}{0pt}{0.5ex}{0ex}

@@

\section{Introduction}
Privacy on the Internet is becoming increasingly important as users realize how vulnerable they are to surveillance and theft of their data.  A recent Pew study listed compromised emails/accounts, harassment, stolen Social Security Numbers, bank information, and credit card numbers as some of the results of online visibility; according to the study, 86\% of internet users have tried to become more anonymous online~\cite{pew}.  Despite this, users do not believe that they have the tools to solve this problem.

@@

\begin{compactitem} \setlength{\itemsep}{.2mm}
\item The Safeplug functions as a HTTP proxy for the browser, which then uses Tor for outgoing traffic.
\item Despite the use of Privoxy as an ad-blocker, the Safeplug does nothing to prevent users' browsers from collecting both first- and third-party tracking cookies, allowing users to be de-anonymized across websites despite the presence of Tor~\cite{arvindpets}.
\item Safeplug users are vulnerable to a Cross-Site Request Forgery (CSRF) attack that allows an attacker external to their home network to modify the Safeplug settings (including silently turning off the use of Tor).
\item A malicious user within the network can modify the Safeplug settings without notifying any other devices on the network.
\item The Safeplug has a higher web request latency than that of the Tor Browser Bundle.
\item The use of the Safeplug provides less protection than the use of the Tor Browser Bundle.
\end{compactitem}

Pogoplug made use of good security principles by using auditable open source software on their device, and has the laudable goal of making online security the standard for more users. However, there are other technologies available that aim to provide the same functionality, such as the Tor Browser Bundle, which can be used free of charge.  In order to determine if there is a market for the Safeplug, we measure the privacy implications between the different technologies.  We show that there is little reason to use the Safeplug over the Tor Browser Bundle; in addition to the Tor network technology used in the Safeplug, the Tor Browser Bundle contains protections against tracking cookies and fingerprinting, making it an improvement over the privacy offerings of the Safeplug.

@@

%\section{Background}
%Safeplug \cite{safeplug}, is a product that launched in December of 2013 from the cloud storage company Pogoplug, that offers any user the option of using Tor \cite{torproject} without having to know about it or how it works.  It allows users to browse the web from their own standard web browser with “complete security and anonymity” for the cheap price of \$49.  Safeplug offers Tor out of the box, with no additional software installation, by sitting between a user's router and the Internet \cite{wired}.  Pogoplug's marketing pitch centers around the protection of users' IP addresses by using Tor \cite{bittech}.

%{\bf Pogoplug.} Pogoplug, a subsidary of Cloud Engines, also offers secure file server or file storage technologies for home networks, called Pogoplug.  Based on our examination of the box discussed below, we suspect that a recent version of the Pogoplug hardware was relabeled as Safeplug and simply uses different software to achieve its newly branded purpose.

\section{Design and Operation of Safeplug}
Safeplug \cite{safeplug} offers any user the option of using Tor \cite{torproject} without having to know about it or how it works.  It allows users to browse the web from their own standard web browser with “complete security and anonymity” for the cheap price of \$49.  Safeplug offers Tor out of the box, with no additional software installation, by sitting between a user's router and the Internet \cite{wired}.  Pogoplug's marketing pitch centers around the protection of users' IP addresses by using Tor \cite{bittech}.

%\subsection{Hardware}
%Before investigating the software, we took apart one of the two Safeplug devices we purchased in order to see the physical components.  Figure~\ref{fig:top} shows the top of the board and Figure~\ref{fig:bottom} shows the bottom.  The board incorporates: (A) an SD card slot, (B) a power connector, (C) a USB slot, (D) an ethernet connector, (E) ethernet transceiver, (F) lan transformer, (G) the Marvell 88F6192 integrated controller, and (H), (I) flash memory.  The Marvell controller is from 2008 and is an ARM SoC~\cite{marvellhw}. 
%\begin{figure*}[tb]
%\centering
%\subfloat[][Top of the board inside the Safeplug device.]{
%  \includegraphics[width=.2\textwidth]{safeplug_listed_top}
%  \label{fig:top}
%}
%\qquad
%\subfloat[][Bottom of the Board inside the Safeplug device.]{
%  \includegraphics[width=.2\textwidth]{safeplug_hardware_new}
%  \label{fig:bottom}
%}
%\caption{Safeplug circuit board after the teardown.  The explanation of the components is in the text.}
%\label{fig:circuit}
%\end{figure*}

%\begin{figure}[ht]
% \centering
% \subfigure[Top of board.]{
%  \includegraphics[width=.2\textwidth]{safeplug_listed_top}
%   \label{fig:top}
%   }
% \subfigure[Bottom of board.]{
%  \includegraphics[width=.2\textwidth]{safeplug_hardware_new}
%   \label{fig:bottom}
%   }
% \label{fig:circuit}
% \caption[Safeplug circuit board after the teardown.  The explanation of the components is in the text.]{%
%  Safeplug circuit board after the teardown.  The explanation of the components is in the text.}
%\end{figure}

\subsection{Software on the Safeplug}
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Software and the corresponding version numbers on the Safeplug as of May 2014.}
\label{versions}
\begin{center}
\small
  \begin{tabular}{|l|c|c|c|}
    \hline
    Safeplug Software & Version & Date & Up To Date\\ \hline
    Linux Kernel & 2.6.31.8 & 2009 & No\\ \hline
    Lighttpd Web Server & 1.4.33 & 2013 & No\\ \hline
    Privoxy Proxy & 3.0.21 & 2013 & Yes\\ \hline
    Tor & 0.2.3.25 & 2012 & No\\ \hline
    Dropbear sshd & v0.52 & 2008 & No\\ \hline
  \end{tabular}
\end{center}
\end{table}

Table \ref{versions} shows the software used by the device, the corresponding version of the software, the date of that version's release, and if it is up to date as of May 2014.  There are many known vulnerabilities in the pieces of software that are not up to date.

@@

This software can be understood by explaining what happens when a user modifies the Safeplug settings page.  Javascript on the settings page generates a POST request to {\tt xspctrl}, which is a script running via CGI in Lighttpd. The CGI handler copies a number of environment variables, and then forks and runs {\tt xspctrl} via {\tt execve} (in the constructed environment). {\tt xspctrl} is a shell script with a method for each settings change; these methods execute any necessary Safeplug binary files (go\_update, go\_upgrade, go\_sshd, or go\_updateexceptions) and then return a HTTP response.

@@

%\subsection{Networking}
%The Lighttpd, Privoxy, and Dropbear software give some indication of the networking services on the device.  We used \texttt{nmap} to scan the ports.  Before the activation of the Safeplug, only ports 80 (HTTP) and 3333 (unknown purpose) are open.  After the activation, port 22 for SSH, port 80 for settings access and port 8080 for http-proxy are open.  When Tor is turned on as a relay, port 9001 is opened as well.  This corresponds with the note on the settings page about Tor relays discussed in Section \ref{port9001} below.

\subsection{Configuration on the Safeplug}
\label{spconfig}
The Safeplug configuration files can be found in \verb!/opt/xce/etc! and include \verb!sp.conf!, \verb!sp_version!, and \verb!sp_torexceptions!.  The first contains all of the configuration details: whether to use Tor, whether to block ads, and whether to act as a Tor relay or exit relay. The version file is used during the call to check for updates in the \verb!xspctrl! script, and the exceptions file is used by the Privoxy configuation to control the whitelist of sites not to connect to via Tor.  These configuration files are read by the scripts in \verb!/opt/xce/etc/init.d! which enable Lighttpd, Privoxy, and Tor.  As expected, Privoxy looks at the \verb!tor!, \verb!ad-block! and \verb!exceptions! configurations, and Tor reads the \verb!sp.conf! file to determine the correct Tor configuration file (regular, relay, or exit relay).

\section{Usability}
Several aspects of the user experience of the Safeplug also affect the security of the device.

@@

One of the topics the TOS discusses is the use of open source software.  A standard term of many open source licenses states that a company that uses the open source software must list the software used and its license, as well as the open source code of their own software that uses the license.  The TOS contains a link to a page that would supposedly comply with this requirement: \url{http://pogoplug.com/home-en-developers-open-source.html} but the link is dead; instead, the reader sees a 404 error \cite{safeplug}.  There is an open source page, which describes several pieces of software used by the Safeplug; however, there is no way to find this page from the Terms of Service or the Safeplug website.

\subsection{Activation and Setup}
%The first step was to plug Safeplug into our router and activate our device.  We followed the simple instructions, activated our device, and then ended on the configurations page.  The configurations page shows a variety of platforms and browsers, shown in Table \ref{table_example}, and links to proxy configuration instructions for each one.  For every browser on every client device that the user wants to protect, they must set up the Safeplug as the browser's HTTP proxy and ensure that the proxy stays set up when the browser is updated or re-installed.

First, we activated the device by following simple instructions.  Next, we followed the configuration instructions based on our specific platform and browser (the options are shown in Table \ref{table_example}) to set up the Safeplug as our browser's HTTP proxy.  The last step was to modify the settings; this page is shown in Figure~\ref{fig:settings}.  We can turn Tor on/off, turn ad-blocking on/off, and turn relay node ability on/off (and if on, an additional option appeared to allow the device to be an exit relay).  Additionally, we can specify ``white-listed'' domains that will be connected to directly even if Tor is turned on, without going through the Tor network.

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{The platforms and browsers that the Safeplug settings page provides instructions for.}
\label{table_example}
\centering
\small
	\begin{tabular}{|c|c|}
	\hline
		Platform & Browsers \\ \hline
		Windows	& Internet Explorer, Chrome, Firefox \\ \hline
		OSX & Safari, Chrome, Firefox \\ \hline
		iOS	& Safari \\ \hline
		Android	& Chrome \\ \hline
	\end{tabular}
\end{table}

\begin{figure}
  \centering
  \includegraphics[width=.5\textwidth]{settings_with_exit}
  \caption{Safeplug settings page.  The last button ``Allow Exit'' only appears if the relay option above has been turned on.}
  \label{fig:settings}
\end{figure}

%\subsection{Explanation of Tor Configuration Options}
%\label{port9001}

%The settings page describes Tor in an extremely basic way:

%\begin{quotation}
%``Safeplug uses the Tor network to secure your Internet connection.  Tor works by routing your Internet through a series of random destinations, much like driving a twisty, complicated route to throw off someone who is following you, making it impossible for websites and organizations to identify the source or destination of Internet traffic.''
%\end{quotation}

%On the other hand, it assumes a much higher level of knowledge about networks for users trying to configure a relay:
%\begin{quotation}
%You must forward inbound traffic on port 9001 to [IP-of-Safeplug]. For help configuring your router, click here.''
%\end{quotation}

%The link provided is to an advertisement-filled and confusing website.

It is important to note that there is no explanation of relay or exit nodes.  Using Safeplug as an exit node has possible legal repercussions.  As an exit relay, all traffic that exits the node can be traced back to the Safeplug's IP address; it is likely that some of this traffic contains illegal information or is part of illicit activities.  The Tor Project recommends not running an exit relay from a user's home.  Considering that the Safeplug is intended for home use, it is a poor design choice to allow the user to use it as an exit relay without providing the user with any contextual information.

%\subsection{Internet Use}
%\label{inetuse}

@@

%Next, we examined popular webpages, with an eye for changes in the user experience.  A user would probably decide not to use Safeplug if they could not read their web pages (due to a different language), or if they could not log into their accounts (some web sites will lock a user out if they try to log in from multiple countries in a short time period).  While browsing the Internet, we experienced some pages in German and Swedish; if a user is not familiar with Tor, they may not understand why this is happening.  We were also prompted with a request to ``Enter the name of the city where you usually sign in'' when we tried to log into our Google account, indicating that Google noticed we were trying to login from an ``unusual'' location.

\subsection{Cookies}  
While browsing the Internet in a fresh browser session, we used FourthParty, a plugin developed by Jonathan Mayer to collect information about cookies and other browsing data, to confirm the presence of first-party cookies.  More interesting and damaging to the user's control over their anonymity would be third-party cookies because the user cannot remove those just by logging out.  Most browsers require a trip to the browser settings to clear cookies (or not have them set in the first place).  When collecting data on the existence of third-party cookies, we analyzed two separate browsing sessions; they were both new sessions with no cookies.  One of the sessions used the ad-block feature of the Safeplug and the other did not.  We found many third-party cookies in both sessions; these included cookies from: abmr.net, bizographics.com, krxd.net, and bluekai.com among many others.  The ad-block functionality on the Safeplug reduced, but did not eliminate, these third-party cookies.

@@

\subsection{Browser Fingerprinting}
We used Panopticlick~\cite{panopticlick} to examine the fingerprint of a freshly installed Firefox browser running through the Safeplug proxy.  Panopticlick found the browser to be unique, which means that websites that did fingerprinting could very accurately track, correlate, and de-anonymize user traffic without knowing the IP address or even storing a cookie.  The presence of the Safeplug, as an HTTP proxy, should be completely undetectable by the fingerprinting service because HTTP is designed to make proxies transparent.  Unlike the Tor Browser, Safeplug users do not have the fingerprints of other users of the service to help hide their fingerprints.  Allowing the user to use their own browsers significantly increases the amount of variation and customization between users and therefore the likelihood of having a unique fingerprint.

\subsection{Latency}
If the latency of web requests using the Safeplug is noticeably longer than that of normal Internet use, users may be deterred from using the device.  Similarly, if turning Tor on, but not ad-blocking, adds a significant time delay, the user may only turn on the ad-blocking feature (without Tor).  We recorded the time for a web request on a variety of settings, shown in Figure~\ref{fig:latency2}.

%\begin{itemize} \setlength{\itemsep}{.2mm}
%\item Plain Firefox (no use of the Safeplug device)
%\item Firefox, no Tor, no ad-blocking (traffic running through the Safeplug device)
%\item Firefox, Tor, no ad-blocking
%\item Firefox, Tor, ad-blocking
%\item Firefox, no Tor, ad-blocking
%\item Tor Browser Bundle with Safeplug (all settings off)
%\item Tor Browser Bundle
%\end{itemize}

@@

\section{Privoxy vs. Tor Browser Bundle}
The Safeplug uses two primary technologies: Tor and Privoxy.  The Tor Project has developed the Tor Browser Bundle, which is a free custom browser that uses Tor as well as other protection mechanisms to help preserve a user's privacy.  The Tor Browser Bundle may be a better solution than the Safeplug if it has fewer privacy implications.  The differentiating factor between the Safeplug and the Tor Browser Bundle is the use of Privoxy; in order to determine the effectiveness of the Safeplug in comparison to that of the Tor Browser Bundle, we must measure the value of Privoxy.  We ran a measurement study of the privacy implications of the use of Firefox, Firefox with Privoxy, and the Tor Browser Bundle; our data was collected by running crawls on the Alexa Top 100 sites in each of the specified browsers~\cite{alexa}.  All browser configurations were modified with Pagestats \cite{pagestats} and Cookie Manager+ \cite{cookiemonster} to aggregate information about third party requests, javascript objects, flash objects, and third party cookies.  Table \ref{tbb} shows the per page fraction of: third party domains accessed, javascript objects received from third parties, flash objects received from third parties, and cookies received from third parties.

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Privacy implications of using Firefox, Privoxy, or the Tor Browser Bundle; the numbers represent the fraction of the corresponding privacy implications per page.}
\label{tbb}
\centering
\small
	\begin{tabular}{| p{1.85cm} | p{1.3cm} | p{1.25cm} | p{.7cm} | p{1cm} |}
	\hline
		Configuration & Third Party Domains & Javascript & Flash & Cookies \\ \hline
		Plain Firefox	& 0.64 & 0.01 & 0.01 & 0.88 \\ \hline
		Privoxy & 0.72 & 0.00 & 0.01 & 0.84 \\ \hline
		Tor Browser	& 0.58 & 0.01 & 0.00 & 0.00 \\ \hline
	\end{tabular}
\end{table}

It is clear that the Tor Browser Bundle had the fewest privacy implications in most categories. The one category where Privoxy performed better than the Tor Browser Bundle is in the number of javascript objects received from third parties; this can be attributed to the fact that our measurements were taken using the default settings for the Tor Browser Bundle, which allows javascript (NoScript is disabled)~\cite{torproject}.  This is explained on the Tor Project's website; they explain that disabling javascript causes some web pages to break, making the browser less user-friendly.  The user has the option to enable javascript by simply clicking a button.  This shows that the Tor Browser is a less expensive alternative to the Safeplug, and provides more privacy protections.

\section{Vulnerabilities}
As we discovered during our software analysis, the Safeplug has a remote procedure call (RPC) capability.  This is a script called \verb!xspctrl! found in \verb!/opt/xce/html/svc!.  Functional calls to this script include the ability to enable and disable all of the Safeplug settings, including Tor, ad block, and Tor relay.  None of them require any authentication.

\begin{figure}
  \centering
  \includegraphics[width=.5\textwidth]{disabletor2}
  \caption{Disabling Tor as an RPC attack.}
  \label{disable}
\end{figure}

@@

Since the RPC version of the attack just involves basic Internet tools (the ability to send a POST request), the attacker could also be any kind of device on the local network, or the local gateway itself, if it is compromised.

@@

\section{Related Work}
To our knowledge, there has been no other study analyzing the security of Pogoplug's Safeplug device.  However, there has been much prior research on Tor and fingerprinting.
